This project follows the guide to codebook creation by Adrian Gadient-Brügger at <https://www.adrianbruegger.com/post/simple-codebook/>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages('tidyverse')
install.packages('sjlabelled')
install.packages('psych')
library(tidyverse)
library(sjlabelled)
library(psych)
```

Load some example data:

```{r}
library(haven) # package to read files from popular statistical software packages such as SPSS, SAS, Stata
data <- read_sav("https://mmi.psycho.unibas.ch/r-toolbox/data/Cars.sav") # import data
```

The following commands work with labeled data, but the sjlabelled package has documentation [here](https://cran.r-project.org/web/packages/sjlabelled/index.html) that includes examples of how to add labels.

```{r}
get_label(data) # show content of variables (what the variable measures)

# which returns for example:
# MPG               
# "Miles per Gallon"

get_labels(data) # show value labels (what the different answer options mean)
# note: the value labels are not used for this very simple codebook.

# which returns for example:
# $CYLINDER
# [1] "3 Cylinders" "4 Cylinders" "5 Cylinders" "6 Cylinders" "8 Cylinders"
```

Suppose that you want to extract the labels from a data set: the following code does so using the tibble library, included in tidyverse.

```{r}
# extract labels from dataframe and store as new object
simple_codebook <- enframe(get_label(data))

# use more informative column names
colnames(simple_codebook) <- c("variable_id", "item_text")

# Show the new data frame
simple_codebook
```

To include basic summary statistics of the data set along with the variables and labels, one can do this using the psych library:

```{r}
# get descriptive statistics and select those of interest
descriptives <- data %>% describe() %>% as_tibble() %>% select("n","min","max","mean")
# add stats to codebook 
simple_codebook <- cbind(simple_codebook,descriptives)
```

The following code will save the codebook in .csv format:

```{r}
# write to csv
write.csv(simple_codebook,file="simple_codebook.csv", na="", row.names=FALSE) 
```
